Spatial Reasoning and Statistical Graphics

### 2014-10-13 Paper/Draft1/TestingVisualAptitude.Rnw
Looking at the relationship between cognitive tests sans lineups: we don't have 4 separate factors here!

<<correlations, fig.cap="Scree plot of principle component analysis of performance on the different test batteries.", out.width=".5\\linewidth", fig.height=4.5, fig.width=7.5, comment="|", warning=F, message=F>>=
cor(ans.summary[,c("lineup","card_rot", "fig_class", "folding", "vis_search")])
# using scaled version right now, should be changed to unscaled once the scores are internally scaled.
pca <- prcomp(ans.summary[,c("lineup", "card_rot", "fig_class", "folding", "vis_search")], scale=T)
summary(pca)
screeplot(pca)
@

>>>>

<<correlations, fig.cap="Scree plot of principle component analysis of performance on the different test batteries.", out.width=".5\\linewidth", fig.height=4.5, fig.width=7.5, comment="|", warning=F, message=F>>=
cor(ans.summary[,c("lineup","card_rot", "fig_class", "folding", "vis_search")])
# using scaled version right now, should be changed to unscaled once the scores are internally scaled.
pca <- prcomp(ans.summary[,c("lineup", "card_rot", "fig_class", "folding", "vis_search")], scale=F)
summary(pca)
screeplot(pca)
pca$rotation

# Just using the 4 cognitive tests and ignoring the lineups...
pca.cog.tests <- prcomp(ans.summary[,c("card_rot", "fig_class", "folding", "vis_search")])
summary(pca.cog.tests)
screeplot(pca.cog.tests)
pca.cog.tests$rotation
@
